A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2023-07-31 tidyindex.qmd
Update Intro paragraph 4

In this work, we develop a data pipeline framework where indexes from different domains can be built from. Based on the pipeline, an R package, tidyindex, is developed for practitioners to construct indexes and understand how an index responds to changes in different components in the pipeline. This work provides researchers actively developing new indexes with tools to evaluate the proposed indexes on their robustness for wider adoption. It also helps index analysts to diagnose an index to identify its weakness for methodology improvement.

>>>>

In this work, we aim at providing statistical and computational methods to develop a data pipeline framework for constructing and customize indexes using data. As a companion the R package, tidyindex, is developed  to construct and explore different. Furthermore, the tidyindex package can be used to explore the effects of changes on index definition, index construction steps, and construction methods. This work provides researchers actively developing new indexes or aiming at improving indexes with the tools to easily modify and evaluate indexes. It also helps index analysts diagnose indexes, carry out sensitivity analysis to assess small perturbations in the index, and identify potential weaknesses for methodology improvement.
